---
title: "Rx_resistance"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Rx_resistance}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(dplyr)
library(ggplot2)
library(ape)
library(rotl)
library(remotes)
library(datelife)


```

## Reading in the antibiotic resistance on neisseria file.
```{r}
Rxresistance <- read.csv(file = "../data-raw/metadata.csv")
head(Rxresistance)
colnames(Rxresistance)
rownames(Rxresistance)
na.omit(Rxresistance)
```

```{r, fig.height = 22, fig.width = 15}
tre1 <- read.tree(file = "../data-raw/segata_2013.tre")
plot(tre1, cex = 0.1)
mtext(text = "Segata 2013 OpenTree tree")
```

## This is a phylogenetic tree comprised of the sub-species belonging to the genus, Neisseria. As you can see there are multiple divergences within the genus, which can be explained through the physiological properites of each species. There are some species that have developed higher virulence while others can be mutualistic with other kinds of organisms. Although, it is very difficult to see, Neisseria Gonorrheae is located near the top the tree along with its related sub-species such as meningitidis and lactamica. There are numerous polyphyletic groups, with only one outgroup. 
